D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-06 ootavacuous.tex
Combine Introduction and Background
Aside from its first sentence, the Introduction section contains
essentially no information that isn't already present in the table of
contents.  While "Tell them what you're going to tell them, then tell
them, then tell them what you've told them" might be a good strategy for
an oral presentation where listeners can't easily refer back to earlier
portions, it's wasteful and distracting for written work.

Therefore I removed all the redundant material from the Introduction,
and since only one sentence remained, I decided to combine it with the
following Back

\section{Introduction}
\label{sec:Introduction}

This paper shows that compiler-based C++ implementations subject to
reasonable real-world constraints cannot exhibit OOTA cycles.
Section~\ref{sec:Background}
provides background on the problem of OOTA cycles, including a
brief summary of prior work.
Section~\ref{sec:OOTA and Semantic Dependencies}
motivates a shift in definition of OOTA cycle and reviews properties of
semantic dependencies, showing that these properties are a function of
executions rather than simply of the source code.
This leads into
Section~\ref{sec:What is an Execution?},
which describes properties of abstract and hardware executions, along
with the relationship between the two.

This in turn leads to
Section~\ref{sec:C++ Compilers}, which describes properties of the tool
commonly used to create hardware executions with the proper relationship
to a given set of abstract executions, namely  the compiler.
Section~\ref{sec:Hardware Dependencies, Instruction Ordering, and the
Fundamental Property}
then combines hardware dependencies and instruction ordering to arrive
at the fundamental property of semantic dependencies, which
Section~\ref{sec:A Definition of Semantic Dependency} uses to
arrive at a definition of the term ``semantic dependency''.

This sets the stage for
Section~\ref{sec:Real-World Constraints}
to bring real-world constraints to bear, starting with the laws of
physics, informally demonstrating that these constraints prevent
OOTA cycles containing only volatile and quasi-volatile atomics from
occurring in undefined-behavior-free C++ programs running on correctly
constructed C++ compiler-based implementations that are restricted to
single-threaded analysis in our current universe.

Finally,
Section~\ref{sec:Future Directions}
lists a few possible future directions for this work and
Section~\ref{sec:Conclusion}
presents concluding remarks.

\section{Background}
\label{sec:Background}

This section provides a brief overview of the OOTA problem, followed
by an equally brief summary of prior work in this area, and ending
with a quick overview of the \co{herd7} tool that will be used to
evaluate litmus tests.

>>>>

\section{Introduction and Background}
\label{sec:Introduction}

This paper shows that compiler-based C++ implementations subject to
reasonable constraints on how they treat accesses to atomic objects
cannot exhibit out-of-thin-air (OOTA) cycles.
It follows that these implementations hardly need to take any special
action to avoid OOTA.
In fact, for many compilers the constraints boil down to a simple
``Don't invent or duplicate atomic accesses'', which is probably
something the compiler wouldn't do anyway.

We begin with a brief overview of the OOTA problem, followed
by an equally brief summary of prior work in this area, and ending
with a quick overview of the \co{herd7} tool that will be used to
evaluate litmus tests.
